Late Pleistocene stone artefact technology at Mau A, Yen Bai, Norther Vietnam

### 2022-02-24 analysis/paper/paper.Rmd
Changed "Reduction categories were based upon dorsal cortex percentages were discretized based upon standard cut points" to "Dorsal cortex percentages discretized upon standard cut points were used to create reduction categories" in methods section
Further edits to wording. Removed "It should also be noted that" in results section

  Reduction categories were based upon dorsal cortex percentages were discretized based upon standard cut points. Flakes with no dorsal cortex were categorized as tertiary flakes, those with up to a dorsal cortex percentage of 50% were considered secondary and those with a dorsal cortex value greater than 50% were considered primary (Bradbury & Carr 1995). Mass clusters were generated using univariate k-means, with the end result being 6 mass clusters, with mass cluster 1 having the least mass on average and 6 having the greatest mass on average. Univariate k-means is a non-hierarchical clustering technique that creates a set number of groups equal to k, with points being assigned to groups in such a manner that the total distances between each point and mean of the group in minimized. For more information on univariate k-means, Papageorgiou (2020) examines the various different statistical techniques (including k-means) that can be applied in an archaeological setting, specifically in the study of ceramics.

@@

  It should also be noted that shape variation is not equal along both primary dimensions. For flakes in all three dorsal cortex classes, the largest differences between each inter-nested is along the first primary dimension. Slight differences are seen along the second primary dimension, with an increasing amount of variation as one goes from primary to secondary to tertiary flakes, but these changes are minor when compared to the larger changes seen in the first primary dimension.

>>>>

Dorsal cortex percentages discretized upon standard cut points were used to create reduction categories. Flakes with no dorsal cortex were categorized as tertiary flakes, those with up to a dorsal cortex percentage of 50% were considered secondary and those with a dorsal cortex value greater than 50% were considered primary (Bradbury & Carr 1995). Mass clusters were generated using univariate k-means, with the end result being 6 mass clusters, with mass cluster 1 having the least mass on average and 6 having the greatest mass on average. Univariate k-means is a non-hierarchical clustering technique that creates a set number of groups equal to k, with points being assigned to groups in such a manner that the total distances between each point and mean of the group in minimized. For more information on univariate k-means, Papageorgiou (2020) examines the various different statistical techniques (including k-means) that can be applied in an archaeological setting, specifically in the study of ceramics.

@@

  Shape variation is not equal along both primary dimensions. For flakes in all three dorsal cortex classes, the largest differences between each inter-nested is along the first primary dimension. Slight differences are seen along the second primary dimension, with an increasing amount of variation as one goes from primary to secondary to tertiary flakes, but these changes are minor when compared to the larger changes seen in the first primary dimension.
